Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-05-09 cleanpaper/pedestrian_forecasting_iros_2017.tex
Everything is done

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/MHD_results.eps}
	\caption{A comparison of the MHD from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms at longer time scales since they assume that the end point of the trajectory is unknown.}
	\label{fig:mhd_vs_time}
	\vspace*{-0.7cm}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/MHD_results.eps}
	\caption{A comparison of the MHD from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms at longer time scales since they assume that the end point of the trajectory is known.}
	\label{fig:mhd_vs_time}
	\vspace*{-0.7cm}
\end{figure}

### 2017-05-09 paper/pedestrian_forecasting_iros_2017.tex
Everything is done

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/MHD_results.eps}
	\caption{\rtext{A comparison of the MHD from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms at longer time scales since they assume that the end point of the trajectory is unknown.}}
	\reversemarginpar\marginnote{\#4.8}
	\label{fig:mhd_vs_time}
	\vspace*{-0.7cm}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/MHD_results.eps}
	\caption{\rtext{A comparison of the MHD from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms at longer time scales since they assume that the end point of the trajectory is known.}}
	\reversemarginpar\marginnote{\#4.8}
	\label{fig:mhd_vs_time}
	\vspace*{-0.7cm}
\end{figure}
